The symmetry problem of the \textit{Fermi} and eROSITA bubbles: A proof-of-concept study

### 2022-02-24 paper.tex
update

 Moreover, the close-up view (right column in \Cref{fig__profile}) of profiles\
 demonstrates that there is a sharp pressure jump at $z=3.62$ kpc,\
 indicating that the pressure jump is an expanding reverse shock.\
 The high density upstream of the reverse shock requires\
 an even higher density downstream.\
 Continuing outward, the higher density must match with low density further downstream;\
 thus there exists a dense shell (3.62--3.75 kpc) associated with a contact discontinuity ($z=3.75$ kpc).

 The turbulent plasma is therefore bracketed between the downstream of reverse shock\
 and of the outermost forward shock, thus heating the turbulent plasma up considerably.

>>>>

 Moreover, the close-up view (right column in \Cref{fig__profile}) of profiles\
 demonstrates that there is a sharp pressure jump on the edge of the innermost bubbles ($z=3.62$ kpc),\
 indicating that the innermost bubbles are an expanding reverse shock.\
 The high density upstream of the reverse shock requires\
 an even higher density downstream.\
 Continuing outward, the higher density must match with low density further downstream;\
 thus there exists a dense shell (3.62--3.75 kpc) associated with a contact discontinuity ($z=3.75$ kpc).
 The turbulent plasma is therefore bracketed between the downstream of reverse shock\
 and of the outermost forward shock, thus heating the turbulent plasma up considerably.
